---
title: "Think Believe 2 (free response)"
output: 
  html_notebook:
    toc: true
    toc_float: true
---

```{r setup}
knitr::opts_chunk$set(echo = F, message = F)
```
kable
In this notebook we analyze the second "think/believe" task, in which participants completed a series of fill-in-the-blanks with free responses.


```{r}
source("./scripts/dependencies.R")
source("./scripts/custom_funs.R")
source("./scripts/var_recode_contrast.R")
```

```{r}
d2_raw <- read_xlsx("../data/ThinkBelieve2_organized.xlsx", sheet = "V1&V2 no dupes") %>%
  # ensure no duplicates
  group_by(thb2_subj) %>%
  top_n(1, thb2_batc) %>% 
  ungroup() %>%
  mutate(thb2_ctry = factor(thb2_ctry, levels = levels_country))
```

```{r}
key2 <- read_xlsx("../data/ThinkBelieve2_organized.xlsx", sheet = 1)[1,] %>% 
  data.frame() %>%
  # get rid of extra qualtrics questions
  select(-c(StartDate:UserLanguage)) %>%
  t() %>% 
  data.frame() %>% 
  rownames_to_column("question") %>%
  rename(question_text = ".") %>%
  # get rid of white space
  mutate(question_text = gsub("\\s+", " ", question_text)) %>%
  # hand code question categories
  mutate(category = case_when(
    grepl("final paper", question_text) |
      grepl("highway into town", question_text) |
      grepl("grocery store", question_text) |
      grepl("chemistry book", question_text) |
      grepl("cooking noodles", question_text) ~ "life fact",
    grepl("praying to God", question_text) |
      grepl("angels deliver", question_text) |
      grepl("go to Heaven", question_text) |
      grepl("changed water", question_text) |
      grepl("human sins", question_text) ~ "Christian religious",
    grepl("cycle of death", question_text) |
      grepl("Buddha found spiritual", question_text) |
      grepl("lotus flower bloomed", question_text) |
      grepl("ghosts suffer", question_text) |
      grepl("burning incense", question_text) ~ "Buddhist religious",
    grepl("moon goes around", question_text) |
      grepl("Barack Obama", question_text) |
      grepl("using batteries", question_text) |
      grepl("Brazil", question_text) |
      grepl("ancient Roman", question_text) ~ "well-known fact",
    grepl("octopus", question_text) |
      grepl("John Brown", question_text) |
      grepl("taller mountain", question_text) |
      grepl("species of fish", question_text) |
      grepl("contains more copper", question_text) ~ "esoteric fact",
    TRUE ~ NA_character_)) %>%
  mutate(category = factor(category, 
                           levels = c("Christian religious", 
                                      "Buddhist religious", 
                                      "well-known fact", 
                                      "esoteric fact", 
                                      "life fact")),
         super_cat = case_when(grepl("fact", category) ~ "fact",
                               grepl("religious", category) ~ "religious",
                               TRUE ~ NA_character_),
         super_cat = factor(super_cat, levels = c("religious", "fact"))) %>%
  rownames_to_column("order") %>%
  mutate(order = as.numeric(order),
         question_text = gsub("‚Äô", "'", question_text),
         question_text_short = gsub("^.*that ", "...", question_text),
         var_name = names(d2_raw[names(d2_raw) != "thb2_version"]))
```

```{r}
d2 <- d2_raw %>%
  filter(thb2_ctry %in% levels_country) %>%
  mutate(thb2_ctry = factor(thb2_ctry, levels = levels_country),
         thb2_demo_sex = factor(thb2_demo_sex,
                                levels = c("Male", "Female", "Other")), 
         thb2_demo_age = as.numeric(as.character(thb2_demo_age))) %>%
  mutate_at(vars(thb2_demo_regp, thb2_demo_olang),
            funs(factor(., levels = c("NO", "YES")))) %>%
  mutate_at(vars(thb2_demo_rely, thb2_demo_impr, thb2_demo_imsn), 
            funs(factor(., levels = 1:7))) %>%
  mutate(thb2_demo_wors = factor(thb2_demo_wors, 
                                 levels = c("Never", 
                                            "Once a year or less",
                                            "A few times a year",
                                            "Once or twice a month",
                                            "Every week or more often")),
         thb2_demo_bgod = factor(thb2_demo_bgod,
                                 levels = c("Not at all believe",
                                            "Believe slightly",
                                            "Believe moderately",
                                            "Believe strongly")),
         thb2_demo_bbuh = factor(thb2_demo_bbuh,
                                 levels = c("Not at all believe",
                                            "Believe slightly",
                                            "Believe moderately",
                                            "Believe strongly")),
         thb2_demo_bosp = factor(thb2_demo_bosp,
                                 levels = c("Not at all believe",
                                            "Believe slightly",
                                            "Believe moderately",
                                            "Believe strongly")),
         thb2_demo_atsn = factor(thb2_demo_atsn,
                                 levels = c("There is no such thing as supernatural forces or beings",
                                            "We cannot know if there are supernatural forces and beings",
                                            "There might be supernatural forces and beings",
                                            "Supernatural forces and beings exist but we cannot know what they are like",
                                            "There definitely are supernatural forces and beings"))) %>%
  mutate_at(vars(thb2_demo_rely, thb2_demo_impr, thb2_demo_wors, thb2_demo_bgod, 
                 thb2_demo_bbuh, thb2_demo_bosp, thb2_demo_atsn, thb2_demo_imsn), 
            funs(num = as.numeric(.) - 1)) %>%
  mutate(religion = case_when(
    thb2_demo_regp_1_TEXT %in% c("Anglican", 
                                 "Anglican/SDA",
                                 "AoG",
                                 "A.O.G youth group", 
                                 "Anuchon Church", 
                                 "AOG: Youth", 
                                 "Apostolic", 
                                 "Bible Church & CMC Church",
                                 "Bible church and Presbyterian church",
                                 "Black Campus Ministry",
                                 "Campus crusade for Christ",
                                 "Catholic Christian",
                                 "Catholic Church",
                                 "cell group Anuchon",
                                 "CF, Youth Ministry etc.",
                                 "Chorus youth",
                                 "Christian", 
                                 "Christian house church",
                                 "Christian - Methodist",
                                 "Christian - Pentecost", 
                                 "Christian - Roman Catholic",
                                 "Christian (Catholic)", 
                                 "Christian (Pentecost)",
                                 "Christian (Potters hand)",
                                 "Christian (Roman)", 
                                 "Christian church in Sop Tia",
                                 "Christian Fellowship Group (CF)", 
                                 "Christianity", 
                                 "Christianity (overcomers and Congress Int. Church)",
                                 "Christianity (Roman Catholic)", 
                                 "Christianity (Roman)", 
                                 "Christians on Campus SJSU",
                                 "Church",
                                 "church",
                                 "Church Youth",
                                 "Church Youth and Religious Singing Group",
                                 "church youths", 
                                 "Church, Youth fellowship",
                                 "Church: Sunday School + Services",
                                 "Community Prayer group", 
                                 "Community Prayer Group",
                                 "D.R.E.A.M Campus Ministry",
                                 "Emalus religious group, student life association",
                                 "Epauto church (Port Vila)", 
                                 "Father's House", 
                                 "Fathers house",
                                 "Fellowship",
                                 "friend group",
                                 "Glorious church people",
                                 "Glourise Church going and pray for sick people",
                                 "Go to Catholic church every Sunday",
                                 "Go to church every Sunday", 
                                 "got to church",
                                 "go to church",
                                 "group of Youth",
                                 "House church", 
                                 "House church of Christian",
                                 "I am part or member of Potoroki youth",
                                 "ICOMB", 
                                 "Jehova's Witnesses",
                                 "Jehovah's Witnesses",
                                 "joy with Municipality group", 
                                 "Just Youth's",
                                 "Kids prayer warrior",
                                 "Korean Campus Crusade for Christ?",
                                 "KYB - Knowing Your Bible",
                                 "LDS",
                                 "LDS Mormon",
                                 "Leader",
                                 "Leader of the Youth",
                                 "Living water, Heram praise", 
                                 "Listen to sermon",
                                 "local churches",
                                 "Mae Ka Boo Church",
                                 "Member of the youth, children class teacher",
                                 "Missonettes",
                                 "Mormon helping hands",
                                 "NTM Youth", 
                                 "only P.R.C",
                                 "Pastor and Apostle",
                                 "Pathfinder, Ambassador, Youth",
                                 "Pathway Ministry", 
                                 "praise & worship, visitation, combine service, youth, choir practice",
                                 "Pray warrior",
                                 "Praying Sunday",
                                 "Presbertent", 
                                 "Presbyterian", 
                                 "Presbyterian Church",
                                 "Pulse", 
                                 "Roman Catholic",
                                 "Roman Catholic (technically)",
                                 "Scripture Union", 
                                 "SDA Youth",
                                 "singing",
                                 "Siyon Group/ like caregroup",
                                 "Student life (USP)", 
                                 "sunday school",
                                 "sunday school, youth etc",
                                 "Sunday School, Bible study and Youth",
                                 "Sunday School, Youth",
                                 "Teacher for Sabbth School",
                                 "Ward Choir, Elder's quorem", 
                                 "Watchnight service",
                                 "Watchnight service ordination",
                                 "Words Christian fellowship",
                                 "Yes kawariki S.D.A Church",
                                 "Yes, Prayer group, Church Instrumentalis",
                                 "Yes! Church youth (drumer)",
                                 "Yes! - youth group/ministry -children ministry",
                                 "Young single adults", 
                                 "youth",
                                 "Youth", 
                                 "Youth Activities",
                                 "Youth Fellowship", 
                                 "Youth group", 
                                 "Youth Group",
                                 "Youth member", 
                                 "Youth Member",
                                 "Youth Members",
                                 "Youth, Church Band and Women's Ministry",
                                 "Youth, Sunday School",
                                 "Youth, Sunday school", 
                                 "Youth, Sunday School, etc...",
                                 "Youth/Men's Fellowship",
                                 "Youths (Port Vila) Anglican",
                                 "(Youth)",
                                 "youths") ~ "Christian",
    thb2_demo_regp_1_TEXT %in% c("Buddhism", 
                                 "Buddhism club",
                                 "Buddhist", 
                                 "Buddhist camping",
                                 "Buddhist Camping",
                                 "Buddhist Club",
                                 "Buddhist Sunday",
                                 "Buddhist, make merit in temple, go to temple",
                                 "Chant / Merit / Listening to Buddhist's teaching",
                                 "facebook village temple",
                                 "Go to neighbor temple", 
                                 "Go to temple",
                                 "Going to temple", 
                                 "Guan Yin Citta (created by an Australian Chinese",
                                 "holy day",
                                 "Holy day",
                                 "make merit", 
                                 "make merit in holy day",
                                 "Make merit",
                                 "Meditation",
                                 "meditation camping",
                                 "Merit give food to monk", 
                                 "Merit, going to temple in holy day",
                                 "Merit group",
                                 "Monk",
                                 "Temple",
                                 "to make merit, listening to Buddhist is teaching",
                                 "to temple") ~ "Buddhist",
    is.na(thb2_demo_regp_1_TEXT) |
      thb2_demo_regp_1_TEXT %in% c("mdata", "Missing Data", "not trans", 
                                   "Not trans", "none") ~ NA_character_,
    TRUE ~ "Other"
  ))

contrasts(d2$thb2_ctry) = contrast_country
```

Note: There are some subjective calls here, and translation issues. For now, I've used a combination of automatic "lemmatization" and hand-coding to do my best to code whether responses should count as "believe" (e.g., including obvious cases like "believes" and "believed"; including Bislama "belif" and "bilif" and other spellings).

As of 2020-01-22, I have two versions of these variables -- one that only includes responses that are strictly "believe" and one that also includes cases that involve the word "believe" (e.g., "firmly believes," "does not believe") -- and likewise for think. The looser interpretations are called `believeX` (or "belief\*") and `thinkX` (or "think\*").

```{r}
d2_long <- d2 %>%
  gather(question, response, thb2_ghostshunger:thb2_obama) %>%
  mutate(response_lemma = lemmatize_strings(tolower(response)),
         response_lemma = gsub("\\( ", "", response_lemma),
         response_lemma = gsub(" \\)", "", response_lemma)) %>%
  mutate(response_lemma2 = case_when(
    response_lemma %in% c("talem", "talemaot", "talm", "blo talem", 
                          "talemout", "bin talem") ~ "say",
    response_lemma %in% c("luk", "look", "lukim", "luk save", "luk vision",
                          "lukum", "bin ko luk", "lok") ~ "see",
    response_lemma %in% c("believe", "belief", 
                          "beliv", "belivs", "belived", 
                          "belivm", "belivem", "belivim",
                          "belif", "belifs", "belifed",
                          "belif", "belifem", "belifim",
                          "biliv", "bilivs", "bilived",
                          "bilivm", "bilivem", "bilivim",
                          "bilif", "bilifs", "bilifed",
                          "bilifm", "bilifem", "bilifim",
                          "belive", "belives", "belived",
                          "bilive", "bilives", "bilived",
                          "beleive", "beleives", "beleived",
                          "beleivm", "beleivem", "beleivim",
                          "biliviem", "beliviem",
                          "beiv", "beives", "beived", 
                          "beivm", "beivem", "beivim",
                          "beleif", "beleifs", "beleifed",
                          "beleifm", "beleifem", "beleifim", 
                          "believem", "wu belive") ~ "believe",
    response_lemma %in% c("biliv strong", "blindly believe", "deeply believe",
                          "firmly believe", "surely believe", 
                          "wrongly believe") ~ "[adverb] believe",
    response_lemma %in% c("does not believe", "doesn't believe",
                          "do not believe", "don't believe",
                          "didn't believe",
                          "no believem") ~ "do not believe",
    response_lemma %in% c("think", "tingting", "tink", "thnks", "tinks",
                          "because she think", "she think", "thing", "ting",
                          "think right that", "think that", "think think",
                          "thinkthink", "use to think") ~ "think",
    response_lemma %in% c("tingbaot", "tingboat", "ting bot", "tingbaut",
                          "tingbot", "tingibaot", "tinkbaot", "thingbaot", 
                          "thingbaut") ~ "think about/remember",
    response_lemma %in% c("think of") ~ "think of",
    response_lemma %in% c("does not think", "doesn't think", 
                          "do not think", "don't think", 
                          "didn't think", "never think", "not think") ~ "do not think",
    response_lemma %in% c("XX") ~ "[adverb] think",
    response_lemma %in% c("save", "saveh", "sae") ~ "know",
    response_lemma %in% c("no save", "nosave", "no sae", "nosae", 
                          "no bin save", 
                          "does not know", "doesn't know", 
                          "do not know", "don't know",
                          "didn't know") ~ "do not know",
    response_lemma %in% c("wantem", "wante", "wantm") ~ "want",
    response_lemma %in% c("harem", "stap harem") ~ "hear",
    response_lemma %in% c("tokbaot", "tok bot", "tokbaout", "talkboat", 
                          "takboat", "tokbaut", "tokabout") ~ "describe/discuss",
    response_lemma %in% c("ridim", "readim", "readm", "ridem", "readem", 
                          "redem") ~ "read",
    response_lemma %in% c("kiaman", "kieman") ~ "lie",
    response_lemma %in% c("lanem") ~ "learn",
    response_lemma %in% c("trastem", "trustem") ~ "trust",
    response_lemma %in% c("confemem", "confirmem") ~ "confirm",
    response_lemma %in% c("faenem", "fainem", "finem", "be fainem", "finiem") ~ "find",
    response_lemma %in% c("fraet", "fright") ~ "fear",
    response_lemma %in% c("laekem", "likem", "laikem") ~ "like",
    response_lemma %in% c("no likem") ~ "do not like",
    response_lemma %in% c("sek") ~ "be shaken",
    response_lemma %in% c("saprais", "sapras", "saprias") ~ "be surprised",
    response_lemma %in% c("tijim", "titjim") ~ "teach",
    response_lemma %in% c("wari") ~ "worry",
    response_lemma %in% c("dream", "drim", "droem") ~ "dream",
    response_lemma %in% c("enkarej") ~ "encourage",
    response_lemma %in% c("explenem") ~ "explain",
    response_lemma %in% c("faenemaot", "faenmaot", "fainem out", "fainmoat",
                          "fainmaot", "faenamaot", "faenemaut", 
                          "fainem aot", "fanemaut", "finemaot", 
                          "finemout", "faenem maot", "faenemaat", "faenemoat",
                          "faenemout", "finem aot") ~ "find out",
    response_lemma %in% c("fogatem", "forgetem", "fogetem", "fogatem", "foget",
                          "foketem", "forget", "foket", "foketom") ~ "forget", 
    response_lemma %in% c("from") ~ "because of",
    response_lemma %in% c("hop") ~ "hope",
    response_lemma %in% c("imagin", "imaginem") ~ "imagine",
    response_lemma %in% c("infomem", "informem", "informen") ~ "inform",
    response_lemma %in% c("kasem") ~ "receive",
    response_lemma %in% c("kros") ~ "angry",
    response_lemma %in% c("kwesten", "questenem") ~ "question",
    response_lemma %in% c("notisim") ~ "notice",
    response_lemma %in% c("riconizem", "riconizen") ~ "recognize",
    response_lemma %in% c("rimembarem", "rememba", "remember") ~ "remember",
    response_lemma %in% c("ripot", "reportam", "ribotem") ~ "report",
    response_lemma %in% c("singaot") ~ "call",
    response_lemma %in% c("sowem", "soem") ~ "show",
    response_lemma %in% c("withnessem") ~ "witness",
    response_lemma %in% c("kes") ~ "case",
    response_lemma %in% c("studi", "study", "stady", "stadi") ~ "study",
    response_lemma %in% c("havem") ~ "have",
    response_lemma %in% c("jes save") ~ "come to know",
    response_lemma %in% c("save finis") ~ "already know",
    response_lemma %in% c("understanem", "antastanem") ~ "understand",
    response_lemma %in% c("no understanem") ~ "do not understand",
    response_lemma %in% c("agri") ~ "agree",
    response_lemma %in% c("askem") ~ "ask",
    response_lemma %in% c("bin identifi") ~ "identify",
    response_lemma %in% c("discoverem", "diskararem") ~ "discover",
    response_lemma %in% c("folemap") ~ "follow up",
    response_lemma %in% c("rielaesm", "realaesem", "realise", 
                          "realizem") ~ "realize",
    response_lemma %in% c("no rielaesm") ~ "did not realize",
    response_lemma %in% c("raetem", "writem", "raitem", "ritem", 
                          "biritingbut") ~ "write",
    response_lemma %in% c("traem") ~ "try",
    response_lemma %in% c("watchem", "watchm", "wajem") ~ "watch",
    response_lemma %in% c("tingse", "tung se") ~ "express an opinion",
    response_lemma %in% c("rao") ~ "argue",
    response_lemma %in% c("ansa", "ansarem") ~ "answer",
    response_lemma %in% c("jekem") ~ "check",
    response_lemma %in% c("olsem") ~ "all-same",
    response_lemma %in% c("serchem") ~ "search",
    response_lemma %in% c("sua") ~ "be sure",
    response_lemma %in% c("promes") ~ "promise",
    response_lemma %in% c("wet") ~ "wait",
    response_lemma %in% c("krae") ~ "cry",
    response_lemma %in% c("prae") ~ "pray",
    response_lemma %in% c("ring") ~ "call",
    response_lemma %in% c("use to she fill this way") ~ "feel", 
    response_lemma == "mdata" ~ NA_character_,
    TRUE ~ response_lemma
  )) %>%
  mutate(think = ifelse(response_lemma2 %in% c("think", "thought"), T, F),
         thinkX = ifelse(grepl("think", response_lemma2) |
                           grepl("thought", response_lemma2), T, F)) %>%
  mutate(believe = ifelse(response_lemma2 %in% c("believe", "belief"), T, F),
         believeX = ifelse(grepl("belie", response_lemma2), T, F)) %>%
  mutate(response_cat3 = case_when(think == T ~ "think",
                                   believe == T ~ "believe",
                                   !is.na(response) ~ "other response",
                                   TRUE ~ NA_character_),
         response_cat3 = factor(response_cat3, 
                                levels = c("other response", "think", "believe")),
         responseX_cat3 = case_when(thinkX == T ~ "think*",
                                    believeX == T ~ "believe*",
                                    !is.na(response) ~ "other response",
                                    TRUE ~ NA_character_),
         responseX_cat3 = factor(responseX_cat3,
                                 levels = c("other response", "think*", "believe*")),
         response_cat = recode_factor(as.character(believe), 
                                      "FALSE" = "other", "TRUE" = "believe"),
         responseX_cat = recode_factor(as.character(believeX), 
                                       "FALSE" = "other", "TRUE" = "believeX")) %>%
  left_join(key2 %>% select(-question) %>% rename(question = var_name))

contrasts(d2_long$thb2_ctry) = contrast_country
# contrasts(d2_long$category) = contrast_category
contrasts(d2_long$category) = contrast_category_orth
contrasts(d2_long$super_cat) = contrast_super_cat
```

```{r}
# implement exclusion criteria and rename country variable
d2 <- d2 %>% 
  filter(thb2_ordr == "Yes", thb2_attn == "Pass") %>%
  rename(country = thb2_ctry)

d2_long <- d2_long %>% 
  filter(thb2_ordr == "Yes", thb2_attn == "Pass") %>%
  rename(country = thb2_ctry)
```


# Overview

From the preregistration ([link](https://aspredicted.org/p6iy3.pdf)):

> "Our overarching hypothesis for the present study is that [...] other languages will have an epistemic verb that is more likely to be used for religious attitude reports (similar to English “believe”) and a different epistemic verb that is more likely to be used for matter-of-fact attitude reports (similar to English “think”). 
> 
> For this study, we are examining five languages in five regions of interest: (i) Mandarin in China; (ii) Thai in Thailand; (iii) Bislama (an English-based creole
language) on the Melanesian Island of Vanuatu; (iv) Fante in Ghana; and (v) American English in the Bay Area, California. 
> 
> We thus have five more specific sub-hypotheses. For each of the first four languages / regions of interest, we hypothesize that a set of words or phrases exists whose usage parallels the difference between usage of “think” and “believe” in American English, with one word or phrase (the “think” analogue) being used for more matter-of-fact attitude reports and the other (the “believe” analogue) being more likely to be used for religious attitude reports. That gives us our first four sub-hypotheses: that Mandarin, Thai, Bislama and Fante speakers will each use two different words in a manner parallel to the use of
“think” and “believe” in an American English setting as identified by Heiphetz, Landers, and Van Leeuwen. Our fifth sub-hypothesis is that the Bay Area portion of the study will replicate the results of the earlier study of Heiphetz, Landers, and Van Leeuwen."


<p style="color:darkred">**KW EXECUTIVE SUMMARY (2020-01-20): We replicated the original finding in the US (and the findings of Think Believe 1): participants were more likely to write in "believe" for religious than fact questions. We found the same pattern in all five countries/langauges included in this study.**</p>

<p style="color:darkred">**As in Think Believe 1, the pattern was somewhat weaker in Ghana/Fante than in other countries/languages. In Think Believe 1, the pattern was stronger in Thailand/Thai (and no stronger or weaker in China/Mandarin or Vanuatu/Bislama); in contrast, in this study it was stronger in China/Mandarin, weaker in Vanuatu/Bislama, and no stronger or weaker Thailand/Thai. I suspect these patterns are largely accounted for by the fact that so few participants in Ghana and especially Vanuatu spontaneously used the word "believe" in their free responses.**</p>


# Samples

Before we begin, it's important to note that we had unequal sample sizes by country:

```{r}
d2_raw %>% count(thb2_ctry)
```

However, `r d2_raw %>% filter(thb2_ordr == "No") %>% count() %>% as.numeric()` participants completed this task after completing other surveys, and an additional `r d2_raw %>% filter(thb2_ordr == "Yes", thb2_attn == "Fail") %>% count() %>% as.numeric()` failed the attention check. In the following analyses I will exclude these participants, leaving us with the following samples:

```{r}
d2 %>% count(country)
```

```{r}
sample_size_d2 <- d2 %>% 
  count(country) %>% 
  data.frame() %>%
  mutate(country_n = paste0(country, " (n=", n, ")"),
         country_n = reorder(country_n, as.numeric(country)))
```


# Plots

We'll begin by plotting responses of "think(s)/thought" (red) vs. "believe(s)/believed" (turquoise) vs. other responses (gray) to get an overall sense of any patterns in the data.

```{r}
three_cols <- c("gray", gg_color_hue(2))
```

## By superordinate category

```{r, fig.width = 3, fig.asp = 0.5}
d2_long %>%
  left_join(sample_size_d2) %>%
  # ggplot(aes(x = super_cat, fill = response_cat3)) +
  ggplot(aes(x = super_cat, fill = responseX_cat3)) + # includes "does not X", "[adverb] X"
  facet_grid(. ~ country_n, scales = "free", space = "free") +
  geom_bar(position = "fill", alpha = 0.7, color = "black", size = 0.1) +
  # geom_hline(yintercept = 0.5, lty = 2) +
  scale_fill_manual(values = three_cols) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "top") +
  labs(x = "category", y = "proportion", fill = "response")
```

## By category

```{r, fig.width = 3, fig.asp = 0.5}
d2_long %>%
  left_join(sample_size_d2) %>%
  # ggplot(aes(x = category, fill = response_cat3)) +
  ggplot(aes(x = category, fill = responseX_cat3)) + # includes "does not X", "[adverb] X"
  facet_grid(. ~ country_n, scales = "free", space = "free") +
  geom_bar(position = "fill", alpha = 0.7, color = "black", size = 0.1) +
  # geom_hline(yintercept = 0.5, lty = 2) +
  scale_fill_manual(values = three_cols) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "top") +
  labs(x = "category", y = "proportion", fill = "response")
```

## By question

```{r, fig.width = 6, fig.asp = 0.7}
d2_long %>%
  left_join(sample_size_d2) %>%
  # ggplot(aes(x = reorder(str_wrap(question_text_short, 40), order), 
  #            fill = response_cat3)) +
  ggplot(aes(x = reorder(str_wrap(question_text_short, 40), order), 
             fill = responseX_cat3)) + # includes "does not X", "[adverb] X"
  facet_grid(country_n ~ category, scales = "free", space = "free") +
  geom_bar(position = "fill", alpha = 0.7, color = "black", size = 0.1) +
  # geom_hline(yintercept = 0.5, lty = 2) +
  scale_fill_manual(values = three_cols) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "top",
        plot.margin = (unit(c(0.2, 0.2, 0.2, 1.8), "cm"))) +
  labs(x = "category", y = "proportion", fill = "response")
```


# Analysis: KW without looking at preregistration

These analyses directly parallel the way I analyzed the Think Believe 1 data before looking at the preregistration. Again, I think these analyses are valuable because they're a little more efficient than the preregistered analyses -- no need for follow-up tests -- and they directly test the question of whether the effect of interest varies across countries/langauges.

As of 2020-01-22, I'm now using the more lenient "believe\*" variable in these analyses.

Technical note: Unless specified otherwise, all of these analyses use "effect coding" for categorical variables (e.g., country, category of question) -- meaning that each country/langauge is compared to the "grand mean" collapsing across all countries/languages. Because of degrees of freedom issues, each analysis only compares 4 of the 5 countries to the grand mean -- by default, I've left out the comparison of the US/English to the grand mean, but stats for that comparison could easily be calculated (if we left out another country/language instead). This is just to say that you won't see statements like "The effect was exaggerated in the US relative to other countries," although they might be true.

## KW Analysis #1

First, I used a mixed effects logistic regression predicting how likely a participant was to write "believe" based on the superordinate category of the question ("religious" questions or "fact" questions), the country they were in/language they were using (US/English, Ghana/Fante, Thailand/Thai, China/Mandarin, or Vanuatu/Bislama), and an interaction between them, with a maximal random effects structure (random interpcepts and slopes by subject, and random intercepts by question). This analysis gives me a sense of (1) Whether participants were more likely to write "believe" for religious questions than fact questions, and whether this tendency varied by country/language, controlling for the fact that the overall rates of circling "believe" might vary by country/language (and accounting for individual differences and differences across individual questions).

Note that this analysis treats responses of "think" as the same as any other non-"believe" response -- I'm just trying to predict how likey the participant was to write in "believe."

```{r, echo = T}
r2.1 <- lmer(believeX ~ super_cat * country 
             + (1 + super_cat | thb2_subj) + (1 | question), 
             # + (1 + super_cat || thb2_subj) + (1 | question), 
             # + (1 + super_cat | thb2_subj), 
             # + (1 + super_cat || thb2_subj), 
             # + (1 | thb2_subj) + (1 | question), 
             data = d2_long)
```

```{r}
regtab_fun(r2.1, std_beta = T) %>% regtab_style_fun(row_emph = c(2, 7:10))
```

```{r, include = F}
regtab_ran_fun(r2.1, subj_var = "thb2_subj") %>% regtab_style_fun()
```

The effects of primary interest are in bold:

- **Category (religious)**: Collapsing across countries/languages, participants were indeed more likely to say "believe" for "religious" questions, echoing the forced choice results of Think Believe 1.
- Country (Gh.): Participants in Ghana were generally less likely than other participants to say "believe," collapsing across question categories. (This is in contrast to Think Believe 1, in which they were more likely to circle "believe.")
- Country (Th.): Participants in Thailand were no more or less likely than other participants to say "believe," collapsing across question categories. (This is in contrast to Think Believe 1, in which they were less likely to circle "believe.")
- Country (Ch.): Participants in China were no more or less likely than other participants to say "believe," caollapsing across question categories. (They did not differ from the grand mean in Think Believe 1.)
- Country (Vt.): Participants in Vanuatu were no more or less likely than other participants to say "believe," collapsing across question categories. (They did not differ from the grand mean in Think Believe 1.)
- **Category (religious) x Country (Gh.)**: The difference in rates of "believe" responses between question categories was smaller in Ghana than in other countries, echoing the forced choice results of Think Believe 1. 
- **Category (religious) x Country (Th.)**: The difference in rates of "believe" responses between question categories was no smaller or larger in Thailand than in other countries. (In Think Believe 1, the difference was exaggerated in Thailand.)
- **Category (religious) x Country (Ch.)**: The difference in rates of "believe" responses between question categories was larger in China than in other countries. (In Think Believe 1, this difference did not differ from the difference in other countries.)
- **Category (religious) x Country (Vt.)**: The difference in rates of "believe" responses between question categories was smaller in Vanuatu than in other countries. (In Think Believe 1, this difference did not differ from the difference in other countries.)

**Take-away: The predicted effect is evident in this dataset, as it was in Think Believe 1. It appears to be exaggerated in China and diminished in Ghana and Vanuatu, a pattern which differs from Think Believe 1.**

## KW Analyses #1a-1e (by country)

Next, I did this same analysis within each country/langauge alone (using the most maximal random effect structure that converged across all countries/languages). 

```{r, echo = T}
# note: using most maximal common random effects structure
r2.1_us <- lmer(believeX ~ super_cat + 
                  # (1 + super_cat | thb2_subj) + (1 | question),
                  # (1 + super_cat || thb2_subj) + (1 | question),
                  # (1 | thb2_subj) + (1 | question),
                  (1 + super_cat | thb2_subj),
                  # (1 + super_cat || thb2_subj),
                  # (1 | thb2_subj),
                data = d2_long %>% filter(country == "US"))

r2.1_gh <- lmer(believeX ~ super_cat + 
                  # (1 + super_cat | thb2_subj) + (1 | question),
                  # (1 + super_cat || thb2_subj) + (1 | question),
                  # (1 | thb2_subj) + (1 | question),
                  (1 + super_cat | thb2_subj),
                  # (1 + super_cat || thb2_subj), 
                  # (1 | thb2_subj),
                data = d2_long %>% filter(country == "Ghana"))

r2.1_th <- lmer(believeX ~ super_cat + 
                  # (1 + super_cat | thb2_subj) + (1 | question), # failed to converge
                  # (1 + super_cat || thb2_subj) + (1 | question), # failed to converge
                  (1 | thb2_subj) + (1 | question),
                  # (1 + super_cat | thb2_subj),
                  # (1 + super_cat || thb2_subj), 
                  # (1 | thb2_subj),
                data = d2_long %>% filter(country == "Thailand"))

r2.1_ch <- lmer(believeX ~ super_cat + 
                  # (1 + super_cat | thb2_subj) + (1 | question),
                  # (1 + super_cat || thb2_subj) + (1 | question),
                  # (1 | thb2_subj) + (1 | question), # failed to converge
                  (1 + super_cat | thb2_subj),
                  # (1 + super_cat || thb2_subj), 
                  # (1 | thb2_subj),
                data = d2_long %>% filter(country == "China"))

r2.1_vt <- lmer(believeX ~ super_cat + 
                  # (1 + super_cat | thb2_subj) + (1 | question),
                  # (1 + super_cat || thb2_subj) + (1 | question),
                  # (1 | thb2_subj) + (1 | question),
                  (1 + super_cat | thb2_subj),
                  # (1 + super_cat || thb2_subj), 
                  # (1 | thb2_subj),
                data = d2_long %>% filter(country == "Vanuatu"))
```

```{r}
bind_rows(regtab_fun(r2.1_us) %>% mutate(Country = "US"),
          regtab_fun(r2.1_gh) %>% mutate(Country = "Ghana"),
          regtab_fun(r2.1_th) %>% mutate(Country = "Thailand"),
          regtab_fun(r2.1_ch) %>% mutate(Country = "China"),
          regtab_fun(r2.1_vt) %>% mutate(Country = "Vanuatu")) %>%
  select(Country, everything()) %>%
  regtab_style_fun(row_emph = seq(2, 10, 2)) %>%
  collapse_rows(1)
```

The effects of primary interest are in bold, and **the take-away is clear: In every country/language, participants were more likely to say "believe" in "religious" questions than in "fact" questions**.


## KW Analysis #2

In this analysis, I treated country/language as a random rather than fixed effect (with participants nested within countries). 

```{r, echo = T}
r2.2 <- lmer(believeX ~ super_cat 
             # + (1 + super_cat | country/thb2_subj) + (1 | question), # failed to converge
             # + (1 + super_cat || country/thb2_subj) + (1 | question), # failed to converge
             # + (1 + super_cat | country/thb2_subj), # failed to converge
             # + (1 + super_cat || country/thb2_subj), # failed to converge
             # + (1 | country/thb2_subj) + (1 | question), # failed to converge
             + (1 | country/thb2_subj), 
             data = d2_long)
```

```{r}
regtab_fun(r2.2) %>% regtab_style_fun(row_emph = 2)
```

```{r, include = F}
regtab_ran_fun(r2.2, subj_var = "thb2_subj") %>% regtab_style_fun()
```

The effect still holds.

## KW Analysis #3

Finally, I ran a version of this first model looking at 5 categories of questions (rather than 2 superordinate categories): Christian religious, Buddhist religious, well-known fact, esoteric fact, and personal fact. I compared these categories using planned orthogonal contrasts. 

```{r, echo = T}
r2.3 <- lmer(believeX ~ category * country 
             + (1 + category | thb2_subj) + (1 | question), 
             # + (1 + category || thb2_subj) + (1 | question),
             # + (1 + category | thb2_subj), 
             # + (1 + category || thb2_subj), 
             # + (1 | thb2_subj) + (1 | question),
             data = d2_long)
```

```{r}
regtab_fun(r2.3, 
           predictor_var1 = "category_relig_fact", 
           predictor_name1 = "Category (Religious vs. fact)",
           predictor_var2 = "category_relig_C_B",
           predictor_name2 = "Category (Christian vs. Buddhist religious)",
           predictor_var3 = "category_fact_WE_L",
           predictor_name3 = "Category (well-known & esoteric vs. personal fact)",
           predictor_var4 = "category_fact_W_E",
           predictor_name4 = "Category (well-known vs. esoteric fact)") %>% 
  regtab_style_fun(row_emph = c(2:5, 10:25)) %>%
  group_rows("Intercept", start_row = 1, end_row = 1) %>%
  group_rows("Category comparisons", start_row = 2, end_row = 5) %>%
  group_rows("Country comparisons", start_row = 6, end_row = 9) %>%
  group_rows("Interactions: Ghana", start_row = 10, end_row = 13) %>%
  group_rows("Interactions: Thailand", start_row = 14, end_row = 17) %>%
  group_rows("Interactions: China", start_row = 18, end_row = 21) %>%
  group_rows("Interactions: Vanuatu", start_row = 22, end_row = 25)
```

```{r, include = F}
regtab_ran_fun(r2.3, subj_var = "thb2_subj") %>% regtab_style_fun()
```

The first orthogonal contrast compared the two "religious" categories to the three "fact" categories ("Category (Religoius vs. fact)"). This parallels the previous analyses, and the results are similar: Overall, participants were more likely to write "believe" for religious questions than fact questions, and this tendency was diminished in Ghana and Vanuatu, and exaggerated in China.

The second orthogonal contrast compared Christian to Buddhist "religious" questions. Overall, participants were more likely to write "believe" for Christian questions, and this tendency was exaggerated in Vanuatu and diminished in Thailand (partially echoing Think Believe 1).

The third orthogonal contrast compared well-known and esoteric facts, on the one hand, to personal facts, on the other. Overall, there was no reliable difference in rates of "believe" between these groups of questions (in contrast to Think Believe 1, in which participants were more likely to circle "believe" for well-known and esoteric facts). This difference did not vary by country.

The fourth orthogonal contrast compared well-known to esoteric facts.  Overall, there was no reliable difference in rates of "believe" between these groups of questions (in contrast to Think Believe 1, in which participants were more likely to circle "believe" for well-known facts). This difference did not vary by country.

Note that these findings statistically control for differences across samples in the overall rate of writing "believe" (which was generally lower in Ghana).


# Analysis: Based on preregistration

From preregistration:

> "Survey 1: We will conduct a 5 (Site: China vs. Thailand vs. Vanuatu vs. Ghana vs. United States) x 2 (Statement Type: religion vs. fact) mixed ANOVA with repeated measures on the second factor and the proportion of trials on which participants completed sentences using a form the word “believe” (or its respective translation) as the dependent measure. To look for finer-grained differences between different religious and factual statements, we will also conduct a 5 (Site: China vs. Thailand vs. Vanuatu vs. Ghana vs. United States) x 5 (Statement Type: Buddhist religious statements vs. Christian religious statements vs. life facts vs. well-known facts vs. esoteric facts) mixed ANOVA with repeated measures on the second factor and the proportion of trials on which participants completed sentences using a form of the word “believe” (or its respective translation) as the dependent measure. In all cases where omnibus ANOVAs are significant, we will conduct pairwise analyses comparing each statement type with each other statement type and each site with each other site."

```{r, echo = T}
d2_anova <- d2_long %>%
  distinct(thb2_subj, country, super_cat, question, believeX) %>%
  group_by(thb2_subj, country, super_cat) %>%
  summarise(prop_believeX = mean(believeX)) %>%
  ungroup() %>%
  mutate(thb2_subj = factor(thb2_subj))

contrasts(d2_anova$country) <- contrast_country
contrasts(d2_anova$super_cat) <- contrast_super_cat
```

## Prereg Analysis #1

Here is the first preregistered analyis: a 5 (country) x 2 (question category) mixed ANOVA with repeated measures on the second factor and the proportion of trials on which participants wrote "berlieve" as the DV.

```{r, echo = T}
r2.4 <- d2_anova %>%
  anova_test(dv = prop_believeX, 
             wid = thb2_subj, 
             between = country, 
             within = super_cat)

get_anova_table(r2.4)
```

This analysis aligns with the regressions above and with Think Believe 1, suggesting that participants' tendency to write "believe" varied by country/language (`country`) and by question category (`super_cat`), and the difference between question category varied across countries/languages (i.e., there was an interaction: `country:super_cat`).

The preregistration indicated that we'd conduct pairwise follow-up analyses comparing the two question categories and comparing pairs of countires/languages -- but, again, I don't really think we're interested in comparing pairs of countries/languages, so I'm going to skip that for now. Instead, I'll compare the two questions categories within each country/language (to explore the significant interaction), as I did for Think Believe 1.

Here we go:

### Comparing question categories

```{r, echo = T}
r2.5a <- t.test(prop_believeX ~ super_cat, paired = T, d2_anova); r2.5a
```

Collapsing across countries/languages, **participants wrote significantly more "believe" responses for questions in the religious category (`r 100 * (r2.5a$estimate[1] %>% round(2))`%) than they did for questions in the fact category (`r 100 * (r2.5a$estimate[2] %>% round(2))`%)**.

### Comparing question categories within countries/languages

```{r, echo = T}
# US
r2.5b_us <- t.test(prop_believeX ~ super_cat, paired = T,
                   d2_anova %>% filter(country == "US")); r2.5b_us

# Ghana
r2.5b_gh <- t.test(prop_believeX ~ super_cat, paired = T,
                   d2_anova %>% filter(country == "Ghana")); r2.5b_gh


# Thailand
r2.5b_th <- t.test(prop_believeX ~ super_cat, paired = T,
                   d2_anova %>% filter(country == "Thailand")); r2.5b_th

# China
r2.5b_ch <- t.test(prop_believeX ~ super_cat, paired = T,
                   d2_anova %>% filter(country == "China")); r2.5b_ch

# Vanuatu
r2.5b_vt <- t.test(prop_believeX ~ super_cat, paired = T,
                   d2_anova %>% filter(country == "Vanuatu")); r2.5b_vt
```

**The difference between question categories was significant in each country/language considered alone.**


# Free response data

Here's a very quick pass at looking at the most common words/phrases in these free responses -- I did a quick and dirty "stemming" (converting, e.g., "believe" and "believes" and "believed" all to the stem "believ") but we could look into doing something more sophisticated. Here are the top 5 stems for each question category, by country: 

```{r, include = F}
d2_long %>%
  count(country, super_cat, category, response_lemma2) %>%
  arrange(country, super_cat, category, desc(n))
```

```{r}
d2_long %>%
  count(country, super_cat, category, response_lemma2) %>%
  arrange(country, super_cat, category, desc(n)) %>%
  group_by(country, super_cat, category) %>%
  mutate(percent = paste0(round(n/sum(n), 2) * 100, "%")) %>%
  top_n(5, n) %>%
  ungroup() %>%
  select(country, super_cat, category, response_lemma2, percent, n) %>%
  kable() %>%
  kable_styling() %>%
  collapse_rows(1:3)
```

I think there's lots to discuss here -- e.g., the common use of "know" (which I think is already of interest). Also, the Bislama data appears to be in Bislama (not translated) -- I've included "bilif" (and spelling variants) as "believe" and "ting" (as spelling variants) as "think" in all of the foregoing analyses.

```{r}
top_words <- d2_long %>%
  count(country, response_lemma2) %>%
  group_by(country) %>%
  mutate(prop = n/sum(n)) %>%
  top_n(6, prop) %>%
  ungroup() %>%
  group_by(response_lemma2) %>%
  summarise(n = sum(n),
            prop = sum(prop)/5) %>%
  ungroup() %>%
  arrange(desc(prop)) %>%
  mutate(order = 1:nrow(.))
```

```{r}
four_cols <- c("gray", "khaki", gg_color_hue(2))
```

```{r, fig.width = 7, fig.asp = 0.5}
d2_long %>%
  filter(response_lemma2 %in% top_words$response_lemma2) %>%
  count(country, super_cat, #category, 
        response_lemma2) %>%
  complete(response_lemma2, nesting(country, super_cat), fill = list(n = 0)) %>%
  arrange(super_cat, #category, 
          country, desc(n)) %>%
  group_by(country, super_cat) %>% #, category) %>%
  mutate(proportion = round(n/sum(n), 2)) %>%
  ungroup() %>%
  mutate(response_lemma2 = reorder(response_lemma2, desc(n)),
         response_color = case_when(response_lemma2 == "think" ~ "think",
                                    response_lemma2 == "believe" ~ "believe",
                                    response_lemma2 == "know" ~ "know",
                                    TRUE ~ "other"),
         response_color = factor(response_color,
                                 levels = c("other", "know", "think", "believe"))) %>%
  left_join(top_words %>% select(response_lemma2, order)) %>%
  ggplot(aes(x = reorder(response_lemma2, order), 
             y = proportion, fill = response_color)) +
  facet_grid(super_cat ~ country) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = four_cols) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "top") +
  labs(x = "response", y = "proportion", fill = "response type")
```

```{r}
write_csv(d2_long, "../data/thinkbelieve2_freeresponse_kw.csv")
```


# Analysis: Religion and religiosity

## Demographics

First, let's just look at how people in different countries replied to the relevant questions. 

### `thb2_demo_regp`: "Are you a part of any religious group?"

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = country_n, 
             # put NAs on top of bar
             fill = factor(thb2_demo_regp,
                           levels = c(NA, "NO", "YES"), 
                           exclude = NULL))) +
  geom_bar(position = "fill") +
  labs(x = "country", y = "proportion", 
       fill = "Are you a part of any religious group?") +
  theme(legend.position = "top")
```

### `thb2_demo_regp_1_TEXT`: "Are you a part of any religious group? If yes, what group?"

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = country_n, 
             # put NAs on top of bar
             fill = factor(religion,
                           levels = c(NA, "Other", "Christian", "Buddhist"),
                           exclude = NULL))) +
  geom_bar(position = "fill") +
  labs(x = "country", y = "proportion", 
       fill = "...If yes, what group?") +
  theme(legend.position = "top")
```

### `thb2_demo_rely`: "From 1 to 7, how religious are you? (1 = not religious at all, 7 =
extremely religious)"

Seems to have been omitted in Thailand?

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = as.numeric(thb2_demo_rely))) +
  facet_grid(~ country_n) +
  geom_histogram(binwidth = 1) +
  scale_x_continuous(breaks = 1:7, minor_breaks = NULL) +
  labs(x = "From 1 to 7, how religious are you?", 
       y = "count")
```

### `thb2_demo_impr`: "From 1 to 7, how important to you is your religious practice?  (1 = not important at all, 7 = of utmost importance)"

Seems to have been omitted in Thailand?

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = as.numeric(thb2_demo_impr))) +
  facet_grid(~ country_n) +
  geom_histogram(binwidth = 1) +
  scale_x_continuous(breaks = 1:7, minor_breaks = NULL) +
  labs(x = "From 1 to 7, how important to you is your religious practice?", 
       y = "count")
```

### `thb2_demo_wors`: "How often do you attend places of worship?"

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = thb2_demo_wors)) +
  facet_grid(~ country_n) +
  geom_bar() +
  labs(x = "How often do you attend places of worship?", 
       y = "count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

### `thb2_demo_bgod`: "What best describes your level of belief in God?"

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = thb2_demo_bgod)) +
  facet_grid(~ country_n) +
  geom_bar() +
  labs(x = "What best describes your level of belief in God?", 
       y = "count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

### `thb2_demo_bbuh`: "What best describes your level of belief in Buddha?"

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = thb2_demo_bbuh)) +
  facet_grid(~ country_n) +
  geom_bar() +
  labs(x = "What best describes your level of belief in Buddha?", 
       y = "count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

### `thb2_demo_bosp`: "What best describes your level of belief in another spiritual being (other than God or Buddha)?"

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = thb2_demo_bosp)) +
  facet_grid(~ country_n) +
  geom_bar() +
  labs(x = "What best describes your level of belief in another spiritual being (other than God or Buddha)?", 
       y = "count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

### `thb2_demo_atsn`: "What best describes your attitude towards the supernatural?

```{r, fig.width = 3.5, fig.asp = 0.8}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = thb2_demo_atsn)) +
  facet_grid(~ country_n) +
  geom_bar() +
  labs(x = "What best describes your attitude towards the supernatural?", 
       y = "count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

### `thb2_demo_imsn`: "From 1 to 7, how important to you is your attitude toward the supernatural? (1 = not important at all, 7 = of utmost importance)"

```{r}
d2 %>% 
  left_join(sample_size_d2) %>%
  ggplot(aes(x = as.numeric(thb2_demo_imsn))) +
  facet_grid(~ country_n) +
  geom_histogram(binwidth = 1) +
  scale_x_continuous(breaks = 1:7, minor_breaks = NULL) +
  labs(x = "From 1 to 7, how important to you is your attitude toward the supernatural?", 
       y = "count")
```

## Analyses

Now, let's look at how responses to our think/believe questions might have varied depending on religiosity/etc. For now, I'll just focus on a couple of variables that seem to have been answered in reasonable ways.

### `thb2_demo_rely`: “From 1 to 7, how religious are you? (1 = not religious at all, 7 = extremely religious)”

```{r, echo = T}
r2.6 <- lmer(believe ~ super_cat * country * thb2_demo_rely_num
             + (1 + super_cat | thb2_subj) + (1 | question),
             data = d2_long %>% 
               filter(country != "Thailand") %>%
               mutate(thb2_demo_rely_num = scale(thb2_demo_rely_num)),
             contrasts = list(country = "contr.sum"))
```

```{r}
regtab_fun(r2.6, std_beta = T, 
           country_var1 = "country1", country_name1 = "Country (US)",
           country_var2 = "country2", country_name2 = "Country (Ghana)",
           country_var3 = "country3", country_name3 = "Country (China)",
           predictor_var1 = "thb2_demo_rely_num", 
           predictor_name1 = "How religious are you?") %>% 
  regtab_style_fun(row_emph = c(10, 14:16))
```

This analysis suggests that greater religiosity was NOT associated with an increased distinction between religious and fact questions. (Note that this analysis omits participants from Thailand, who did not answer this question about religiosity.)

```{r}
d2_long %>% 
  filter(country != "Thailand") %>%
  group_by(country, thb2_subj, thb2_demo_rely_num, super_cat) %>%
  summarise(believe_prop = mean(believe, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = thb2_demo_rely_num, y = believe_prop, color = super_cat)) +
  facet_grid(. ~ country) +
  geom_jitter(alpha = 0.2, width = 0.1, height = 0.02) +
  geom_smooth(method = "lm") +
  scale_x_continuous(breaks = 0:6, labels = levels(d2$thb2_demo_rely)) +
  theme(legend.position = "top") +
  labs(x = "How religious are you?", y = "Proportion 'believe' responses",
       color = "Category")
```

```{r}
d2_long %>% 
  filter(country != "Thailand") %>%
  group_by(country, thb2_subj, thb2_demo_rely_num, super_cat) %>%
  summarise(believe_prop = mean(believe, na.rm = T)) %>%
  ungroup() %>%
  spread(super_cat, believe_prop) %>%
  mutate(diff = religious - fact) %>%
  ggplot(aes(x = thb2_demo_rely_num, y = diff)) +
  facet_grid(. ~ country) +
  geom_jitter(alpha = 0.2, width = 0.1, height = 0.02) +
  geom_smooth(method = "lm") +
  scale_x_continuous(breaks = 0:6, labels = levels(d2$thb2_demo_rely)) +
  theme(legend.position = "top") +
  labs(x = "How religious are you?", 
       y = "Difference in proportion 'believe' responses\n(religious questions - fact questions)",
       color = "Category")
```

### `thb2_demo_impr`: "From 1 to 7, how important to you is your religious practice?  (1 = not important at all, 7 = of utmost importance)"

```{r, echo = T}
r2.7 <- lmer(believe ~ super_cat * country * thb2_demo_impr_num
             + (1 + super_cat | thb2_subj) + (1 | question),
             data = d2_long %>% 
               filter(country != "Thailand") %>%
               mutate(thb2_demo_impr_num = scale(thb2_demo_impr_num)),
             contrasts = list(country = "contr.sum"))
```

```{r}
regtab_fun(r2.7, std_beta = T, 
           country_var1 = "country1", country_name1 = "Country (US)",
           country_var2 = "country2", country_name2 = "Country (Ghana)",
           country_var3 = "country3", country_name3 = "Country (China)",
           predictor_var1 = "thb2_demo_impr_num", 
           predictor_name1 = "How important is your religious practice?") %>% 
  regtab_style_fun(row_emph = c(10, 14:16))
```

This analysis suggests that more importance placed on religious practice was NOT associated with an increased distinction between religious and fact questions. (Note that this analysis omits participants from Thailand, who did not answer this question about religiosity.)

```{r}
d2_long %>% 
  filter(country != "Thailand") %>%
  group_by(country, thb2_subj, thb2_demo_impr_num, super_cat) %>%
  summarise(believe_prop = mean(believe, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = thb2_demo_impr_num, y = believe_prop, color = super_cat)) +
  facet_grid(. ~ country) +
  geom_jitter(alpha = 0.2, width = 0.1, height = 0.02) +
  geom_smooth(method = "lm") +
  scale_x_continuous(breaks = 0:6, labels = levels(d2$thb2_demo_impr)) +
  theme(legend.position = "top") +
  labs(x = "How important is your religious practice?", y = "Proportion 'believe' responses",
       color = "Category")
```

```{r}
d2_long %>% 
  filter(country != "Thailand") %>%
  group_by(country, thb2_subj, thb2_demo_impr_num, super_cat) %>%
  summarise(believe_prop = mean(believe, na.rm = T)) %>%
  ungroup() %>%
  spread(super_cat, believe_prop) %>%
  mutate(diff = religious - fact) %>%
  ggplot(aes(x = thb2_demo_impr_num, y = diff)) +
  facet_grid(. ~ country) +
  geom_jitter(alpha = 0.2, width = 0.1, height = 0.02) +
  geom_smooth(method = "lm") +
  scale_x_continuous(breaks = 0:6, labels = levels(d2$thb2_demo_impr)) +
  theme(legend.position = "top") +
  labs(x = "How important is your religious practice?", 
       y = "Difference in proportion 'believe' responses\n(religious questions - fact questions)",
       color = "Category")
```

### `thb2_demowors`: "How often do you attend places of worship?"

```{r, echo = T}
r2.8 <- lmer(believe ~ super_cat * country * thb2_demo_wors_num
             + (1 + super_cat | thb2_subj) + (1 | question),
             data = d2_long %>% 
               mutate(thb2_demo_wors_num = scale(thb2_demo_wors_num)))
```

```{r}
regtab_fun(r2.8, std_beta = T, 
           predictor_var1 = "thb2_demo_wors_num", 
           predictor_name1 = "How often do you attend places of worship?") %>% 
  regtab_style_fun(row_emph = c(12, 17:20))
```

This analysis suggests that frequency of attendence was NOT associated with an increased distinction between religious and fact questions. 

```{r}
d2_long %>% 
  group_by(country, thb2_subj, thb2_demo_wors_num, super_cat) %>%
  summarise(believe_prop = mean(believe, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = thb2_demo_wors_num, y = believe_prop, color = super_cat)) +
  facet_grid(. ~ country) +
  geom_jitter(alpha = 0.2, width = 0.1, height = 0.02) +
  geom_smooth(method = "lm") +
  scale_x_continuous(breaks = 0:4, labels = levels(d2$thb2_demo_wors)) +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(x = "How often do you attend places of worship?", 
       y = "Proportion 'believe' responses",
       color = "Category")
```

```{r}
d2_long %>% 
  group_by(country, thb2_subj, thb2_demo_wors_num, super_cat) %>%
  summarise(believe_prop = mean(believe, na.rm = T)) %>%
  ungroup() %>%
  spread(super_cat, believe_prop) %>%
  mutate(diff = religious - fact) %>%
  ggplot(aes(x = thb2_demo_wors_num, y = diff)) +
  facet_grid(. ~ country) +
  geom_jitter(alpha = 0.2, width = 0.1, height = 0.02) +
  geom_smooth(method = "lm") +
  scale_x_continuous(breaks = 0:4, labels = levels(d2$thb2_demo_wors)) +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(x = "How often do you attend places of worship?", 
       y = "Difference in proportion 'believe' responses\n(religious questions - fact questions)",
       color = "Category")
```





